Tampering Detection In Low-Power Smart Cameras

### 2015-05-19 paper.tex
experiments

\subsection{Dataset Description}\label{subsec:Dataset}
\gi{Adriano: Prova a mettere qua le info}
The proposed method have been tested on a dataset of frame sequences in which there were tampering events.
A part of this dataset was taken using a Raspberry Pi with its camera module, and the tampering was introduced by moving the device or putting water on the camera.
The other part of this dataset is made of frame sequences taken from web-cams available on the Internet. 
In these sequences there were a few events of displacements or defocus, but to have a larger set of tampering events we
\subsection{Alternative Approaches}\label{subsec:AlternativeApproaches}
\begin{itemize}
\item Full
\item Adaptive Region
\item Voronoi Regions
\end{itemize}

>>>>

\subsection{Dataset Description}\label{subsec:Dataset}
\gi{Adriano: Prova a mettere qua le info}
The proposed method have been tested on a dataset of frame sequences in which there were tampering events.
A part of this dataset was taken using a Raspberry Pi with its camera module, and the tampering was introduced by moving the device or putting water on the camera.
The other part of this dataset is made of frame sequences taken from webcams available on the Internet. 
In these sequences there were a few events of displacements or defocus, but to have a larger set of tampering events we have simulated them.
In particular we have used gaussian filtering for simulating defocus events, and concatenation of similar sequences for simulating displacement events.\\

\subsection{Alternative Approaches}\label{subsec:AlternativeApproaches}
\begin{itemize}
\item Full
\item Adaptive Region
\item Voronoi Regions
\end{itemize}
